Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-05-24 submission/Sze_Obesity_PeerJ_2016.Rmd
added Pat data table 1 demographics

alpha_tests.summary <- read.table("../data/process/alpha_tests.summary", header=T)
alpha_composite.summary <- read.table("../data/process/alpha_composite.summary")
alpha_power.obs <- read.table("../data/process/alpha_power.observed", 
                              header = T, row.names = 1)
alpha_power.predicted <- read.table("../data/process/alpha_power.predicted", 
                                    header = T)
alpha.data.ALL <- read.table("../data/process/alpha.data", header = T)

@@

#Using a quick for loop to generate the necessary effect size information
variableTested <- seq(1:6)
variables <- colnames(alpha_power.obs)[1:6]
alpha_effectSize <- matrix(nrow=length(rownames(beta_tests.summary)), ncol=length(variableTested))
studies <- rownames(beta_tests.summary)

for(i in variableTested){
  tempdata <- c()
  for(j in studies){
  tempdata <- rbind(tempdata, abs((mean(alpha.data.ALL[which(alpha.data.ALL$dataset == j & alpha.data.ALL$obese == FALSE), variables[i]]) - mean(alpha.data.ALL[which(alpha.data.ALL$dataset == j & alpha.data.ALL$obese == TRUE), variables[i]]))/mean(alpha.data.ALL[, variables[i]]) * 100))
  }
  alpha_effectSize[, i] <- tempdata
}

colnames(alpha_effectSize) <- variables
rownames(alpha_effectSize) <- studies

@@

**Table 1. Summary Demographics of Individuals used in the Meta-analysis.**
```{r Table_1, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}

Study <- as.character(rownames(beta_tests.summary))

Age <- as.character(demographics$meanAge)
AgeSD <- as.character(format(round(
  demographics$SDAge, 2), nsmall = 2))
AgeTable <- paste(Age," (",AgeSD,")", sep="")

Sex <- paste(demographics$females, "|", demographics$males)

Ancestry <- as.character(format(round(
  demographics$ancestry*100, 2), nsmall = 2))

ObeseTotal <- ShannonRRTable$tposH + ShannonRRTable$cposH
ContTotal <- ShannonRRTable$tnegH + ShannonRRTable$cnegH

ObBreakdown <- paste(ContTotal, " | ", ObeseTotal, sep="")

BMI <- paste(demographics$meanBMI, " (", demographics$SDBMI, ")", sep="")

Min <- as.character(demographics$minBMI)

Max <- as.character(demographics$maxBMI)

table1 <- cbind(Study, AgeTable, Sex, Ancestry, ObBreakdown, BMI, Min, Max)
table1[table1=="NA" | table1=="NA | NA" | table1=="NA (NA)" |
         table1=="      NA"] <- "Not Available"

>>>>

alpha_tests.summary <- read.table("../data/process/alpha_tests.summary", header=T)
alpha_composite.summary <- read.table("../data/process/alpha_composite.summary")
alpha_power.obs <- read.table("../data/process/alpha_power.observed", 
                              header = T, row.names = 1)
alpha_power.predicted <- read.table("../data/process/alpha_power.predicted", 
                                    header = T)
alpha.data.ALL <- read.table("../data/process/alpha.data", header = T)
alpha_effectSize <- read.table("../data/process/alpha_EffectSize.summary")

@@

@@

**Table 1. Summary Demographics of Individuals used in the Meta-analysis.**
```{r Table_1, echo=FALSE, message=FALSE, warning=FALSE}

table1 <- read.table("../results/tables/table1.demographics", header=T)
